---
title: "wolf_ega_analysis (01_06_23)"
author: "wd"
date: '2023-04-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center",
               fig.retina = 2,
               fig.width = 10,
			         fig.height=7,
               cache = T,
               cache.lazy = F,
               echo = FALSE,
               message = FALSE,
               warning=FALSE)

```

```{r librairies, echo=FALSE, warning=FALSE}
library(readr)
library(tidyverse)

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

#BiocManager::install("DESeq2")
#BiocManager::install("apeglm")
#install.packages("DESeq2")
library(DESeq2)
library(apeglm)

library(survival)
#install.packages("survminer")
library(survminer)



theme_set(theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")
                         )
custom_theme <- theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")


```


# Importations des datas

```{r}
wolf <- read_tsv("D:/AML_processed_data/RNAseq/raw_counts/Wolf_counts_ega.txt")

wolf<- wolf[,2:138]

wolf<- aggregate( x= wolf ,by= list(wolf$hgnc_symbol),FUN=mean)
rownames(wolf)<- wolf$Group.1
wolf <- wolf[,2:137]

metadata_wolf <- read_tsv("D:/AML_processed_data/RNAseq/clinical_data/metadata_wolf.csv")  %>%
column_to_rownames("ID")

i <- colnames(wolf) 
wolf[ , i] <- apply(wolf[ , i], 2,function(x) as.integer(x))

inter_data<- intersect(colnames(wolf),rownames(metadata_wolf))
```




# Préparation

136 échantillons

```{r analyse shrink}
data_deseq <- wolf[,inter_data]
meta_deseq <- metadata_wolf[inter_data,]

dds <- DESeqDataSetFromMatrix(countData = data_deseq, colData = meta_deseq,design = ~ Sex )

# filtration
keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]


# normalisation median of ratios method

dds <- DESeq(dds)
matrix_wolf_vst <-getVarianceStabilizedData(dds)
```
```{r}
fil_metadata_wolf<-metadata_wolf[colnames(matrix_wolf_vst),]
```

```{r}
# vec_cor_wolf<-cor(x= t(matrix_wolf_vst), y= matrix_wolf_vst['ACLY',])
# vec_cor_wolf<-as.data.frame(vec_cor_wolf)
```

```{r}

annot_wolf<-rownames(matrix_wolf_vst)
save(annot_wolf, file = "annot_wolf.rda")
```



# Signatures

```{r calcul signature}

func_signature <- function(vec_genes, mat_vst,vec_correlation){
  vec_final<- c()
  for (i in colnames(mat_vst)){
    vec_sign <- c()
    for (j in vec_genes){
      vec_sign<-append(vec_sign, mat_vst[j,i]*vec_correlation[j,"V1"])
    }
    vec_final<-append(vec_final,mean(vec_sign))
  }
  return(vec_final)
}

```


##ACLY seul

```{r}
quantile(matrix_wolf_vst["ACLY",], c(0,.33, .66,1))
```

```{r}
wolf_acly_only<- cut(matrix_wolf_vst["ACLY",],
                     #breaks=quant,
                       breaks=c(0, 11.28425, 11.56576,14),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(wolf_acly_only)
```

```{r}
fil_metadata_wolf$ACLY_only<-wolf_acly_only
```

### courbe OS


```{r}
surv_curv_wolf <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ ACLY_only, 
                          data = fil_metadata_wolf)
print(surv_curv_wolf )
```

```{r}
ggsurvplot(surv_curv_wolf,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, ACLY",
          xlab="Time (Months)")
```

### courbe EFS

```{r}
surv_curv_wolf_2 <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ ACLY_only, 
                          data = fil_metadata_wolf)
print(surv_curv_wolf_2 )
```

```{r}
ggsurvplot(surv_curv_wolf_2,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, ACLY",
          xlab="Time (Months)")
```


# Signature all samples  totale

```{r}
load("omni_total_sign.rda")
load("correlation_corces_total.rda")
```

## Totale

```{r}
wolf_tot_signature<-func_signature(omni_total_sign,matrix_wolf_vst,correlation_corces_total)
quantile(wolf_tot_signature, c(0,.33, .66,1)) 
```
```{r}
wolf_tot_signature_continuous<- cut(wolf_tot_signature,
                       breaks=c(0, 2.022308, 2.248395 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(wolf_tot_signature_continuous)
```
```{r}
fil_metadata_wolf$sign_all_tot<-wolf_tot_signature_continuous
```

### courbe OS

```{r}
surv_curv_sign_tot_wolf <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_all_tot, data = fil_metadata_wolf)
print(surv_curv_sign_tot_wolf)
```
```{r}
ggsurvplot(surv_curv_sign_tot_wolf,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, total signature",
          xlab="Time (Months)")
```

### courbe EFS

```{r}
surv_curv_sign_tot_wolf_2 <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_all_tot, data = fil_metadata_wolf)
print(surv_curv_sign_tot_wolf_2)
```

```{r}
ggsurvplot(surv_curv_sign_tot_wolf_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, total signature",
          xlab="Time (Months)")
```

## sIGNATURE all samples POSITIVE

```{r}
vec_top_corr_pos<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 >= 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_pos
```

```{r}
wolf_pos_signature<-func_signature(vec_top_corr_pos,matrix_wolf_vst,correlation_corces_total)
quantile(wolf_pos_signature, c(0,.33, .66,1))
```
```{r}
wolf_pos_signature_continuous<- cut(wolf_pos_signature,
                       breaks=c(0,8.381960, 8.626166, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(wolf_pos_signature_continuous)
```

### courbe OS
```{r}
fil_metadata_wolf$sign_tot_pos<-wolf_pos_signature_continuous
surv_curv_sign_pos_wolf <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_tot_pos, data = fil_metadata_wolf)
print(surv_curv_sign_pos_wolf)
```


```{r}
ggsurvplot(surv_curv_sign_pos_wolf,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, positive signature",
          xlab="Time (Months)") 
```

### courbe EFS

```{r}
surv_curv_sign_pos_wolf_2 <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_tot_pos, data = fil_metadata_wolf)
print(surv_curv_sign_pos_wolf_2)
```

```{r}
ggsurvplot(surv_curv_sign_pos_wolf_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, positive signature",
          xlab="Time (Months)") 
```

## sIGNATURE all samples NEGATIVE

```{r}
vec_top_corr_neg<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 < 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_neg
```

```{r}
wolf_neg_signature<-func_signature(vec_top_corr_neg,matrix_wolf_vst,correlation_corces_total)
quantile(wolf_neg_signature, c(0,.33, .66,1))
```

```{r}
wolf_neg_signature_continuous<- cut(wolf_neg_signature,
                       breaks=c(-10, -8.853824,-8.597729, 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(wolf_neg_signature_continuous)
```

### Courbe OS

```{r}
fil_metadata_wolf$sign_tot_neg<-wolf_neg_signature_continuous

surv_curv_sign_neg_wolf<- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_tot_neg, data = fil_metadata_wolf)
print(surv_curv_sign_neg_wolf)
```


```{r}
ggsurvplot(surv_curv_sign_neg_wolf,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```

### Courbe EFS

```{r}
surv_curv_sign_neg_wolf_2<- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_tot_neg, data = fil_metadata_wolf)
print(surv_curv_sign_neg_wolf_2)
```

```{r}
ggsurvplot(surv_curv_sign_neg_wolf_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```



# Signature AML
```{r}
load("omni_aml_tot.rda")
load("correlation_corces_aml.rda")

omni_aml_tot
```


```{r}
wolf_total_signature<-func_signature(omni_aml_tot,matrix_wolf_vst,correlation_corces_aml)
quantile(wolf_total_signature, c(0,.33, .66,1)) 
```

```{r}
wolf_total_signature_continuous<- cut(wolf_total_signature,
                       breaks=c(0, 2.494740 ,2.708420, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(wolf_total_signature_continuous)
```

```{r}
fil_metadata_wolf$sign_tot_aml<-wolf_total_signature_continuous
```


### courbe OS

```{r}
surv_curv_sign_tot_aml_wolf <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_tot_aml, 
                          data = fil_metadata_wolf)
print(surv_curv_sign_tot_aml_wolf)
```

```{r}
ggsurvplot(surv_curv_sign_tot_aml_wolf,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, total signature",
          xlab="Time (Months)")
```

### Courbe RFS

```{r}
surv_curv_sign_tot_aml_wolf_2 <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_tot_aml,
                          data = fil_metadata_wolf)
print(surv_curv_sign_tot_aml_wolf_2)
```

```{r}
ggsurvplot(surv_curv_sign_tot_aml_wolf_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, total signature",
          xlab="Time (Months)")
```

## sIGNATURE POSITIVE


```{r}
vec_aml_pos<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 >= 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_pos

```

```{r}
wolf_pos_aml_signature<-func_signature(vec_aml_pos,matrix_wolf_vst,correlation_corces_aml)
quantile(wolf_pos_aml_signature, c(0,.33, .66,1)) 
```

```{r}
wolf_pos_aml_signature_continuous<- cut(wolf_pos_aml_signature,
                       breaks=c(0, 7.323753 ,7.574591, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(wolf_pos_aml_signature_continuous)
```

```{r}
fil_metadata_wolf$sign_pos_aml<-wolf_pos_signature_continuous
```

### courbe OS

```{r}
surv_curv_sign_pos_aml_wolf <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_pos_aml, 
                          data = fil_metadata_wolf)
print(surv_curv_sign_pos_aml_wolf)
```

```{r}
ggsurvplot(surv_curv_sign_pos_aml_wolf,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, positive signature",
          xlab="Time (Months)")
```

### courbe EFS

```{r}
surv_curv_sign_pos_aml_wolf_2 <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_pos_aml,
                          data = fil_metadata_wolf)
print(surv_curv_sign_pos_aml_wolf_2)

```

```{r}
ggsurvplot(surv_curv_sign_pos_wolf_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, total signature",
          xlab="Time (Months)")
```







## Signature Négative

```{r}
vec_aml_neg<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 < 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_neg
```

```{r}
wolf_neg_signature<-func_signature(vec_aml_neg,matrix_wolf_vst,correlation_corces_aml)
quantile(wolf_neg_signature, c(0,.33, .66,1)) 
```

```{r}
wolf_neg_signature_continuous<- cut(wolf_neg_signature,
                       breaks=c(-10, -7.950893,-7.744970 , 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(wolf_neg_signature_continuous)
```

```{r}
fil_metadata_wolf$sign_neg<-wolf_neg_signature_continuous
```

### courbe OS

```{r}
surv_curv_sign_neg_wolf <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_neg, 
                          data = fil_metadata_wolf)
print(surv_curv_sign_neg_wolf)
```

```{r}
ggsurvplot(surv_curv_sign_neg_wolf,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)")
```



### courbe EFS

```{r}
surv_curv_sign_neg_wolf_2 <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_neg,
                          data = fil_metadata_wolf)
print(surv_curv_sign_neg_wolf_2)
```



```{r}
ggsurvplot(surv_curv_sign_neg_wolf_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of Wolf datas, negative signature",
          xlab="Time (Months)")
```


# Signature LSC
## LSC totale


```{r}
load("omni_LSC_tot.rda")
load("correlation_corces_lsc.rda")

omni_LSC_tot
```

```{r}
wolf_lsc_signature<-func_signature(omni_LSC_tot,matrix_wolf_vst,correlation_corces_lsc)
quantile(wolf_lsc_signature, c(0,.33, .66,1))

```

```{r}
wolf_lsc_signature_continuous<- cut(wolf_lsc_signature,
                       breaks=c(0, 1.2988308,1.4803185 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(wolf_lsc_signature_continuous)
```

```{r}
fil_metadata_wolf$lsc_tot<- wolf_lsc_signature_continuous
```

### courbe OS
```{r}
surv_curv_lsc2 <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ lsc_tot, 
                          data = fil_metadata_wolf)
print(surv_curv_lsc2)
```

```{r}
ggsurvplot(surv_curv_lsc2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)")
```

### courbe EFS

```{r}
surv_curv_lsc <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ lsc_tot,
                         data = fil_metadata_wolf)
print(surv_curv_lsc)
```

```{r}
ggsurvplot(surv_curv_lsc,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of Wolf datas, LSC_tot_90 signature",
          xlab="Time (Months)") 
```

## Lsc positive

```{r}
vec_lsc_pos<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 >= 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))
vec_lsc_pos
```


```{r}
wolf_lsc_signature_pos<-func_signature(vec_lsc_pos,matrix_wolf_vst,correlation_corces_lsc)
quantile(wolf_lsc_signature_pos, c(0,.33, .66,1))

```


```{r}
wolf_lsc_signature_pos_continuous<- cut(wolf_lsc_signature_pos,
                       breaks=c(0, 7.687096, 7.897333 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(wolf_lsc_signature_pos_continuous)
```

```{r}
fil_metadata_wolf$sign_lsc_pos <- wolf_lsc_signature_pos_continuous
```


### courbe OS
```{r}
surv_curv_lsc_pos2 <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_lsc_pos, 
                          data = fil_metadata_wolf)
print(surv_curv_lsc_pos2)
```

```{r}
ggsurvplot(surv_curv_lsc2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)")
```

### courbe EFS

```{r}
surv_curv_lsc_pos <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_lsc_pos ,
                             data = fil_metadata_wolf)
print(surv_curv_lsc_pos )
```

```{r}
ggsurvplot(surv_curv_lsc_pos ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of Wolf datas, LSC_pos_90 signature",
          xlab="Time (Months)") 
```

## Lsc negative

```{r}
vec_lsc_neg<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 < 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))
vec_lsc_neg
```

```{r}
wolf_lsc_signature_neg<-func_signature(vec_lsc_neg,matrix_wolf_vst,correlation_corces_lsc)
quantile(wolf_lsc_signature_neg, c(0,0.33, 0.66,1))

```

```{r}
wolf_lsc_signature_neg_continuous<- cut(wolf_lsc_signature_neg,
                       breaks=c(-10,-6.636084,-6.420211, 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(wolf_lsc_signature_neg_continuous)
```

```{r}
fil_metadata_wolf$sign_lsc_neg <- wolf_lsc_signature_neg_continuous
```



### courbe OS
```{r}
surv_curv_lsc_neg2 <- survfit(Surv(fil_metadata_wolf$`OS [months]`, fil_metadata_wolf$`Death Event`) ~ sign_lsc_neg, 
                          data = fil_metadata_wolf)
print(surv_curv_lsc_neg2)
```

```{r}
ggsurvplot(surv_curv_lsc2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)")
```


### courbe EFS

```{r}
surv_curv_lsc_neg <- survfit(Surv(fil_metadata_wolf$`RFS [months]`, fil_metadata_wolf$`Relapse Event`) ~ sign_lsc_neg , 
                             data =fil_metadata_wolf)
print(surv_curv_lsc_neg )
```

```{r}
ggsurvplot(surv_curv_lsc_neg ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of Wolf datas, LSC_neg_90 signature",
          xlab="Time (Months)") 
```




