---
title: "010623_BEAT"
author: "wd"
date: '2023-02-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center",
               fig.retina = 2,
               fig.width = 10,
			         fig.height=7,
               cache = T,
               cache.lazy = F,
               echo = FALSE,
               message = FALSE,
               warning=FALSE)

```

```{r librairies, echo=FALSE, warning=FALSE}
library(readr)
library(tidyverse)

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

#BiocManager::install("DESeq2")
#BiocManager::install("apeglm")
#install.packages("DESeq2")
library(DESeq2)
library(apeglm)

library(survival)
#install.packages("survminer")
library(survminer)


theme_set(theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")
                         )
custom_theme <- theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")


```


# Import des données


```{r}
beat <- read_tsv("D:/AML_processed_data/RNAseq/raw_counts/BEAT_All_samples_htseq_raw_counts.tsv") %>%
column_to_rownames("gene_name")

i <- colnames(beat) 
beat[ , i] <- apply(beat[ , i], 2,function(x) as.integer(x))

metadata_beat <- read_tsv("D:/AML_processed_data/RNAseq/clinical_data/BEAT_clinical_data_rnaseq_modified.txt") %>%
column_to_rownames("Sample_ID")

```


filtration Vincent
```{r}
#Ligne 138

#v2

BEAT_AML_D0_samples <- metadata_beat %>%
  filter(dxAtInclusion %in% c("ACUTE MYELOID LEUKAEMIA (AML) AND RELATED PRECURSOR NEOPLASMS"),
  !specificDxAtAcquisition %in% c(	"Myeloid sarcoma", "unknown","Essential thrombocythaemia","Atypical chronic myeloid leukaemia, BCR-ABL1 negative", "Myeloid leukaemia associated with Down syndrome", "Plasma cell myeloma"),
       isRelapse == "FAUX",
       Timepoint == "Diagnosis"
) %>% distinct(Sample_ID_1) %>% unlist() %>% as.character()

BEAT_AML_D0_BM_samples <- metadata_beat %>%
  filter(dxAtInclusion %in% c("ACUTE MYELOID LEUKAEMIA (AML) AND RELATED PRECURSOR NEOPLASMS"),
  !specificDxAtAcquisition %in% c(	"Myeloid sarcoma", "unknown","Essential thrombocythaemia","Atypical chronic myeloid leukaemia, BCR-ABL1 negative", "Myeloid leukaemia associated with Down syndrome", "Plasma cell myeloma"),
       isRelapse == "FAUX",
       Timepoint == "Diagnosis",
  specimenType == "Bone Marrow Aspirate"
) %>% distinct(Sample_ID_1) %>% unlist() %>% as.character()

metadata_beat_filtered <- metadata_beat %>% filter(Sample_ID_1 %in% BEAT_AML_D0_BM_samples) %>%
    filter(OS_MONTHS >= 0.5 & is.na(OS_STATUS) == F & grepl("Standard Chemotherapy", cumulativeTreatmentTypes))


```


On ne conserve que les patients BM et D0, donc diagnostiqu
165 échantillons à la fin
```{r}
metadata_beat<- metadata_beat_filtered

inter_data<-intersect(colnames(beat),rownames(metadata_beat))
```






```{r matrice vst}
data_deseq <- beat[,inter_data]
meta_deseq <- metadata_beat[inter_data,]

dds_beat <- DESeqDataSetFromMatrix(countData = data_deseq, colData = meta_deseq,design = ~ AML_diagnosis )

# filtration
keep <- rowSums(counts(dds_beat)) >= 10
dds_beat<- dds_beat[keep,]

dds_beat <- DESeq(dds_beat)

matrix_beat_vst <-getVarianceStabilizedData(dds_beat)
```

```{r}
matrix_beat_vst<-matrix_beat_vst[,rownames(metadata_beat)]
```


```{r}

annot_beat<-rownames(matrix_beat_vst)
save(annot_beat, file = "annot_beat.rda")
```

```{r calcul signature}

func_signature <- function(vec_genes, mat_vst,vec_correlation){
  vec_final<- c()
  for (i in colnames(mat_vst)){
    vec_sign <- c()
    for (j in vec_genes){
      vec_sign<-append(vec_sign, mat_vst[j,i]*vec_correlation[j,"V1"])
    }
    vec_final<-append(vec_final,mean(vec_sign))
  }
  return(vec_final)
}

#essai avec les 3 signatures du groupe AML de Corces



```


## Avec ACLY
```{r}
#matrix_beat_vst["ACLY",]
quantile(matrix_beat_vst["ACLY",], c(0,.33, .66,1))
```

```{r}
beat_acly_only<- cut(matrix_beat_vst["ACLY",],
                       breaks=c(10, 12.37463, 12.70841, 14),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(beat_acly_only)
```

```{r}
metadata_beat$ACLY_only<-beat_acly_only
```

### Courbe OS

```{r}
surv_curv_acly <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ ACLY_only, data = metadata_beat)
print(surv_curv_acly )
```
```{r}
ggsurvplot(surv_curv_acly,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of BEAT datas, ACLY",
          xlab="Time (Months)")
```





# sIGNATURE ALL SAMPLES

## ALL SAMPLES TOTALE


```{r}
load("omni_total_sign.rda")
load("correlation_corces_total.rda")
omni_total_sign
```


```{r}
beat_signature_all_tot<-func_signature(omni_total_sign,matrix_beat_vst,correlation_corces_total)
quantile(beat_signature_all_tot, c(0,.33, .66,1)) 
```


```{r}
beat_all_tot_continuous<- cut(beat_signature_all_tot,
                       breaks=c(0, 2.735721, 2.934305 ,4),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(beat_all_tot_continuous)
```
```{r}
metadata_beat$sign_all_tot<-beat_all_tot_continuous
```

```{r}
surv_curv_all_tot <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_all_tot, data = metadata_beat)
print(surv_curv_all_tot )
```

```{r}
ggsurvplot(surv_curv_all_tot ,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of BEAT datas, total signature ",
          xlab="Time (Months)")
```



## all POSITIVE

```{r}
vec_top_corr_pos<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 >= 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_pos
```

```{r}
beat_pos_signature<-func_signature(vec_top_corr_pos,matrix_beat_vst,correlation_corces_total)

quantile(beat_pos_signature, c(0,.33, .66,1)) 
```

```{r}
beat_pos_signature_continuous<- cut(beat_pos_signature,
                       breaks=c(0, 9.227890 ,9.377159, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(beat_pos_signature_continuous)
```

```{r}
metadata_beat$sign_pos<-beat_pos_signature_continuous
surv_curv_sign_pos <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_pos, data = metadata_beat)
print(surv_curv_sign_pos )
```
```{r}
ggsurvplot(surv_curv_sign_pos,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of BEAT datas, positive signature",
          xlab="Time (Months)") 
```
## sIGNATURE NEGATIVE

```{r}
vec_top_corr_neg<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 < 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_neg
```


```{r}
beat_neg_signature<-func_signature(vec_top_corr_neg,matrix_beat_vst,correlation_corces_total)

quantile(beat_neg_signature, c(0,.33, .66,1))
```

```{r}
beat_neg_signature_continuous<- cut(beat_neg_signature,
                       breaks=c(-10, -8.393098, -8.121123, 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(beat_neg_signature_continuous)
```
```{r}
metadata_beat$sign_neg<-beat_neg_signature_continuous
surv_curv_sign_neg <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_neg, data = metadata_beat)
print(surv_curv_sign_neg )
```

```{r}
ggsurvplot(surv_curv_sign_neg,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of BEAT datas, negative signature",
          xlab="Time (Months)") 
```
# Signature AML

## AML totale

```{r}
load("omni_aml_tot.rda")
load("correlation_corces_aml.rda")

omni_aml_tot


```
```{r}
beat_aml_signature_tot<-func_signature(omni_aml_tot,matrix_beat_vst,correlation_corces_aml)
quantile(beat_aml_signature_tot, c(0,.33, .66,1))

```

```{r}
beat_aml_signature_tot_continuous<- cut(beat_aml_signature_tot,
                       breaks=c(0, 3.468095,3.676824 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(beat_aml_signature_tot_continuous)
```

```{r}
metadata_beat$sign_aml <- beat_aml_signature_tot_continuous
```

### courbe OS

```{r}
surv_curv_sign_aml_tot_beat <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml , data = metadata_beat)
print(surv_curv_sign_aml_tot_beat)
```
```{r}
ggsurvplot(surv_curv_sign_aml_tot_beat ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```

## AML positive
```{r}
vec_aml_pos<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 >= 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_pos
```


```{r}
beat_aml_signature_pos<-func_signature(vec_aml_pos,matrix_beat_vst,correlation_corces_aml)
quantile(beat_aml_signature_pos, c(0,.33, .66,1))

```


```{r}
beat_aml_signature_pos_continuous<- cut(beat_aml_signature_pos,
                       breaks=c(0,  8.445973,8.645352, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(beat_aml_signature_pos_continuous)
```

```{r}
metadata_beat$sign_aml_pos <- beat_aml_signature_pos_continuous
```


### courbe OS

```{r}
surv_curv_sign_aml_pos<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml_pos , data = metadata_beat)
print(surv_curv_sign_aml_pos)
```

```{r}
ggsurvplot(surv_curv_sign_aml_pos ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```

## AML negative


```{r}
vec_aml_neg<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 < 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_neg
```

```{r}
beat_aml_signature_neg<-func_signature(vec_aml_neg,matrix_beat_vst,correlation_corces_aml)
quantile(beat_aml_signature_neg, c(0,0.33, 0.66,1))

```

```{r}
beat_aml_signature_neg_continuous<- cut(beat_aml_signature_neg,
                       breaks=c(-10, -7.309126,-7.080544 , 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(beat_aml_signature_neg_continuous)
```

```{r}
metadata_beat$sign_aml_neg <- beat_aml_signature_neg_continuous
```

#courbe OS

```{r}
surv_curv_sign_aml_neg<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml_neg  , data = metadata_beat)
print(surv_curv_sign_aml_neg)
```

```{r}
ggsurvplot(surv_curv_sign_aml_neg ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```


# Signature LSC
## LSC totale


```{r}
load("omni_LSC_tot.rda")
load("correlation_corces_lsc.rda")

omni_LSC_tot
```



```{r}
beat_lsc_signature<-func_signature(omni_LSC_tot,matrix_beat_vst,correlation_corces_lsc)
quantile(beat_lsc_signature, c(0,.33, .66,1))

```

```{r}
beat_lsc_signature_continuous<- cut(beat_lsc_signature,
                       breaks=c(0, 1.545881,1.807643 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(beat_lsc_signature_continuous)
```
```{r}
metadata_beat$lsc_tot<- beat_lsc_signature_continuous
```


### courbe OS

```{r}
surv_curv_lsc <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ lsc_tot, data = metadata_beat)
print(surv_curv_lsc)
```

```{r}
ggsurvplot(surv_curv_lsc,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_tot_90 signature",
          xlab="Time (Months)") 
```


```{r}

# vecteurs de gènes positifs et négatifs

lsc_cor_pos<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 >= 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))

lsc_cor_neg<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 < 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))

```

## Lsc positive


```{r}
amlcg_lsc_signature_pos<-func_signature(lsc_cor_pos,matrix_beat_vst,correlation_corces_lsc)
quantile(amlcg_lsc_signature_pos, c(0,.33, .66,1))

```


```{r}
amlcg_lsc_signature_pos_continuous<- cut(amlcg_lsc_signature_pos,
                       breaks=c(0, 8.444183,8.644697 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_lsc_signature_pos_continuous)
```

```{r}
metadata_beat$sign_lsc_pos <- amlcg_lsc_signature_pos_continuous
```

### courbe OS

```{r}
surv_curv_lsc_pos <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_lsc_pos , data = metadata_beat)
print(surv_curv_lsc_pos )
```

```{r}
ggsurvplot(surv_curv_lsc_pos ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of BEAT datas, LSC_pos_90 signature",
          xlab="Time (Months)") 
```


## Lsc negative


```{r}
beat_lsc_signature_neg<-func_signature(lsc_cor_neg,matrix_beat_vst,correlation_corces_lsc)
quantile(beat_lsc_signature_neg, c(0,0.33, 0.66,1))

```

```{r}
beat_lsc_signature_neg_continuous<- cut(beat_lsc_signature_neg,
                       breaks=c(-10, -7.025593,-6.691972, 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(beat_lsc_signature_neg_continuous)
```

```{r}
metadata_beat$sign_lsc_neg <- beat_lsc_signature_neg_continuous
```

### courbe OS

```{r}
surv_curv_lsc_neg <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_lsc_neg , data = metadata_beat)
print(surv_curv_lsc_neg )
```

```{r}
ggsurvplot(surv_curv_lsc_neg ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_neg_90 signature",
          xlab="Time (Months)") 
```
