---
title: 'AMLCG analysis (010623)'
author: "wd"
date: '2023-02-20'
output: html_document
---

```{r setup, include=FALSE}
library(markdown)
knitr::opts_chunk$set(fig.align = "center",
               fig.retina = 2,
               fig.width = 10,
			         fig.height=7,
               cache = T,
               cache.lazy = F,
               echo = FALSE,
               message = FALSE,
               warning=FALSE)

```

```{r librairies, echo=FALSE, warning=FALSE}
#remove.packages("")
#install.packages("")

#install.packages("readr")
library(readr)
#install.packages("tidyverse")
library(tidyverse)

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

#BiocManager::install("DESeq2")
#BiocManager::install("apeglm")
#install.packages("DESeq2")
library(DESeq2)
library(apeglm)

#install.packages("survival")
library(survival)
#install.packages("survminer")
library(survminer)

theme_set(theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")
                         )
custom_theme <- theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")


```


# Import_data

```{r}
amlcg <- read_tsv("D:/AML_processed_data/RNAseq/raw_counts/AMLCG_AML_HTSeq_calc_rawcounts.txt") %>%
column_to_rownames("gene_name")

i <- colnames(amlcg) 
amlcg[ , i] <- apply(amlcg[ , i], 2,function(x) as.integer(x))

metadata_amlcg  <- read_tsv("D:/AML_processed_data/RNAseq/clinical_data/AMLCG_meta_curated_full.txt") %>%
column_to_rownames("Sample_ID")

inter_data<-intersect(colnames(amlcg),rownames(metadata_amlcg))
```





# Préparation


```{r creat dds oject}
data_deseq <- amlcg[,inter_data]
meta_deseq <- metadata_amlcg[inter_data,]

dds <- DESeqDataSetFromMatrix(countData = data_deseq, colData = meta_deseq,design = ~ diagnosis )

# filtration
keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]


# normalisation median of ratios method

dds <- DESeq(dds)

matrix_amlcg_vst <-getVarianceStabilizedData(dds)
```
```{r}
matrix_amlcg_vst<-matrix_amlcg_vst[,rownames(metadata_amlcg)]
```


```{r}
# vec_cor_amlcg<-cor(x= t(matrix_amlcg_vst), y= matrix_amlcg_vst['ACLY',])
# vec_cor_amlcg<-as.data.frame(vec_cor_amlcg)
# 
# find_pval_cor <- function(vec_nom_genes, matrix_count){
#   vec_final=c()
#   for(i in vec_nom_genes) {
#     vec_final <- append(vec_final, cor.test(matrix_count["ACLY",], y= matrix_count[i,])$p.value)
#    }
#   return(vec_final)
# }
# 
# pval_all_amlcg<-find_pval_cor(row.names(matrix_amlcg_vst), matrix_amlcg_vst)
# vec_cor_amlcg= cbind(vec_cor_amlcg,pval_all_amlcg )
# 
# vec_cor_amlcg<- vec_cor_amlcg[order(- vec_cor_amlcg[,1] ), , drop= FALSE]
  
```

```{r}

annot_amlcg<-rownames(matrix_amlcg_vst)
save(annot_amlcg, file = "annot_amlcg.rda")
```



# Signatures

```{r calcul signature}

func_signature <- function(vec_genes, mat_vst,vec_correlation){
  vec_final<- c()
  for (i in colnames(mat_vst)){
    vec_sign <- c()
    for (j in vec_genes){
      vec_sign<-append(vec_sign, mat_vst[j,i]*vec_correlation[j,"V1"])
    }
    vec_final<-append(vec_final,mean(vec_sign))
  }
  return(vec_final)
}

#essai avec les 3 signatures du groupe AML de Corces

```


## acly seul

```{r}
#matrix_amlcg_vst["ACLY",]
quantile(matrix_amlcg_vst["ACLY",], c(0,.33, .66,1))
```
```{r}
amlcg_acly_only<- cut(matrix_amlcg_vst["ACLY",],
                       breaks=c(7, 9.495394, 9.976401, 12),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(amlcg_acly_only)
```
```{r}
metadata_amlcg$ACLY_only<-amlcg_acly_only
```

### courbe os

```{r}
surv_curv_acly <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ ACLY_only, data = metadata_amlcg)
print(surv_curv_acly )
```

```{r}
ggsurvplot(surv_curv_acly,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, ACLY",
          xlab="Time (Months)")
```
### courbe efs

```{r}
surv_curv_acly_2 <- survfit(Surv(EFS_MONTHS,EFS_STATUS ) ~ ACLY_only, data = metadata_amlcg)
print(surv_curv_acly_2 )
```

```{r}
ggsurvplot(surv_curv_acly_2,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, ACLY",
          xlab="Time (Months)")
```


# Signature all samples

## Totale

```{r}
load("omni_total_sign.rda")
load("correlation_corces_total.rda")
omni_total_sign
```



```{r}
amlcg_total_signature<-func_signature(omni_total_sign,matrix_amlcg_vst,correlation_corces_total)
quantile(amlcg_total_signature, c(0,.33, .66,1)) 
```

```{r}
amlcg_total_signature_continuous<- cut(amlcg_total_signature,
                       breaks=c(0,2.410825,2.687792,4),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(amlcg_total_signature_continuous)
```

```{r}
metadata_amlcg$sign_tot<-amlcg_total_signature_continuous
```

### courbe os

```{r}
surv_curv_sign_tot_amlcg <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_tot, data = metadata_amlcg)
print(surv_curv_sign_tot_amlcg)
```

```{r}
ggsurvplot(surv_curv_sign_tot_amlcg,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, total signature",
          xlab="Time (Months)") 
```
### courbe EFS

```{r}
surv_curv_sign_tot_amlcg_2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_tot, data = metadata_amlcg)
print(surv_curv_sign_tot_amlcg_2)
```

```{r}
ggsurvplot(surv_curv_sign_tot_amlcg_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, total signature",
          xlab="Time (Months)") 
```

## sIGNATURE all samples POSITIVE

```{r}
vec_top_corr_pos<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 >= 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_pos
```
```{r}
amlcg_total_pos_signature<-func_signature(vec_top_corr_pos,matrix_amlcg_vst,correlation_corces_total)
quantile(amlcg_total_pos_signature, c(0,.33, .66,1)) 
```

```{r}
amlcg_pos_signature_continuous<- cut(amlcg_total_pos_signature,
                       breaks=c(0, 7.697641, 7.947175, 9),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(amlcg_pos_signature_continuous)
```
```{r}
metadata_amlcg$sign_pos<-amlcg_pos_signature_continuous
```

### courbe OS

```{r}
surv_curv_sign_pos_amlcg <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_pos, data = metadata_amlcg)
print(surv_curv_sign_pos_amlcg)
```

```{r}
ggsurvplot(surv_curv_sign_pos_amlcg,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, positive signature",
          xlab="Time (Months)") 
```
### courbe EFS

```{r}
surv_curv_sign_pos_amlcg_2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_pos, data = metadata_amlcg)
print(surv_curv_sign_pos_amlcg_2)
```

```{r}
ggsurvplot(surv_curv_sign_pos_amlcg_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, positive signature",
          xlab="Time (Months)") 
```

## sIGNATURE NEGATIVE

```{r}
vec_top_corr_neg<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 < 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_neg
```


```{r}
amlcg_total_neg_signature<-func_signature(vec_top_corr_neg,matrix_amlcg_vst,correlation_corces_total)
quantile(amlcg_total_neg_signature, c(0,.33, .66,1))
```

```{r}
amlcg_neg_signature_continuous<- cut(amlcg_total_neg_signature,
                       breaks=c(-8, -6.667614, -6.264364, 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_neg_signature_continuous)
```

```{r}
metadata_amlcg$sign_neg<-amlcg_neg_signature_continuous
```

### courbe OS

```{r}
surv_curv_sign_neg_amlcg <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_neg, data = metadata_amlcg)
print(surv_curv_sign_neg_amlcg)
```

```{r}
ggsurvplot(surv_curv_sign_neg_amlcg,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```

### courbe EFS

```{r}
surv_curv_sign_neg_amlcg_2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_neg, data = metadata_amlcg)
print(surv_curv_sign_neg_amlcg_2)
```

```{r}
ggsurvplot(surv_curv_sign_neg_amlcg_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```

# Signature AML
## AML totale

```{r}
load("omni_aml_tot.rda")
load("correlation_corces_aml.rda")

omni_aml_tot


```

```{r}
amlcg_aml_signature_tot<-func_signature(omni_aml_tot,matrix_amlcg_vst,correlation_corces_aml)
quantile(amlcg_aml_signature_tot, c(0,.33, .66,1))

```
```{r}
amlcg_aml_signature_tot_continuous<- cut(amlcg_aml_signature_tot,
                       breaks=c(0, 2.725591 ,2.991601 , 4),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_aml_signature_tot_continuous)
```

```{r}
metadata_amlcg$sign_aml <- amlcg_aml_signature_tot_continuous
```

### courbe OS

```{r}
surv_curv_sign_aml_tot_amlcg <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml , data = metadata_amlcg)
print(surv_curv_sign_aml_tot_amlcg)
```

```{r}
ggsurvplot(surv_curv_sign_aml_tot_amlcg ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```

### courbe EFS

```{r}
surv_curv_sign_aml_tot_amlcg2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_aml, data = metadata_amlcg)
print(surv_curv_sign_aml_tot_amlcg2)
```

```{r}
ggsurvplot(surv_curv_sign_aml_tot_amlcg2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_tot_90 signature",
          xlab="Time (Months)") 
```
## AML positive
```{r}


vec_aml_pos<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 >= 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_pos
```


```{r}
amlcg_aml_signature_pos<-func_signature(vec_aml_pos,matrix_amlcg_vst,correlation_corces_aml)
quantile(amlcg_aml_signature_pos, c(0,.33, .66,1))

```


```{r}
amlcg_aml_signature_pos_continuous<- cut(amlcg_aml_signature_pos,
                       breaks=c(0,  6.701494,7.015224 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_aml_signature_pos_continuous)
```

```{r}
metadata_amlcg$sign_aml_pos <- amlcg_aml_signature_pos_continuous
```


### courbe OS

```{r}
surv_curv_sign_aml_pos<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml_pos , data = metadata_amlcg)
print(surv_curv_sign_aml_pos)
```

```{r}
ggsurvplot(surv_curv_sign_aml_pos ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```



### courbe EFS

```{r}
surv_curv_sign_aml_pos2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_aml_pos , data = metadata_amlcg)
print(surv_curv_sign_aml_pos2 )
```

```{r}
ggsurvplot(surv_curv_sign_aml_pos2 ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_pos_90 signature",
          xlab="Time (Months)") 
```


## AML negative


```{r}
vec_aml_neg<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 < 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_neg
```

```{r}
amlcg_aml_signature_neg<-func_signature(vec_aml_neg,matrix_amlcg_vst,correlation_corces_aml)
quantile(amlcg_aml_signature_neg, c(0,0.33, 0.66,1))

```

```{r}
amlcg_aml_signature_neg_continuous<- cut(amlcg_aml_signature_neg,
                       breaks=c(-10, -5.928138, -5.693276 , 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_aml_signature_neg_continuous)
```
```{r}
metadata_amlcg$sign_aml_neg <- amlcg_aml_signature_neg_continuous
```

#courbe OS

```{r}
surv_curv_sign_aml_neg<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml_neg  , data = metadata_amlcg)
print(surv_curv_sign_aml_neg)
```

```{r}
ggsurvplot(surv_curv_sign_aml_neg ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```



### courbe EFS

```{r}
surv_curv_sign_aml_neg2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_aml_neg , data = metadata_amlcg)
print(surv_curv_sign_aml_neg2 )
```

```{r}
ggsurvplot(surv_curv_sign_aml_neg2 ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_neg_90 signature",
          xlab="Time (Months)") 
```

# Signature LSC

## LSC TOTAL

```{r}
load("omni_LSC_tot.rda")
load("correlation_corces_lsc.rda")

omni_LSC_tot
```
```{r}
amlcg_lsc_signature_tot<-func_signature(omni_LSC_tot,matrix_amlcg_vst,correlation_corces_lsc)
quantile(amlcg_lsc_signature_tot, c(0,.33, .66,1))

```


```{r}
amlcg_lsc_signature_tot_continuous<- cut(amlcg_lsc_signature_tot,
                       breaks=c(0,  1.2636953,1.4289093, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_lsc_signature_tot_continuous)
```

```{r}
metadata_amlcg$sign_lsc_tot <- amlcg_lsc_signature_tot_continuous
```

#courbe OS

```{r}
surv_curv_sign_lsc_tot<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_lsc_tot , data = metadata_amlcg)
print(surv_curv_sign_lsc_tot)
```

```{r}
ggsurvplot(surv_curv_sign_lsc_tot ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```

### courbe EFS

```{r}
surv_curv_sign_lsc_tot2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_lsc_tot , data = metadata_amlcg)
print(surv_curv_sign_lsc_tot2)
```

```{r}
ggsurvplot(surv_curv_sign_lsc_tot2 ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_neg_90 signature",
          xlab="Time (Months)") 

```

## lsc positive

```{r}
vec_lsc_pos<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 >= 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))
vec_lsc_pos
```


```{r}
amlcg_lsc_signature_pos<-func_signature(vec_lsc_pos,matrix_amlcg_vst,correlation_corces_lsc)
quantile(amlcg_lsc_signature_pos, c(0,.33, .66,1))

```


```{r}
amlcg_lsc_signature_pos_continuous<- cut(amlcg_lsc_signature_pos,
                       breaks=c(0, 6.671293,6.866607 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_lsc_signature_pos_continuous)
```

```{r}
metadata_amlcg$sign_lsc_pos <- amlcg_lsc_signature_pos_continuous
```


#courbe OS

```{r}
surv_curv_sign_lsc_pos<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_lsc_pos , data = metadata_amlcg)
print(surv_curv_sign_lsc_pos)
```

```{r}
ggsurvplot(surv_curv_sign_lsc_pos,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```


### courbe EFS

```{r}
surv_curv_sign_lsc_pos2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_lsc_pos , data = metadata_amlcg)
print(surv_curv_sign_lsc_pos2)
```

```{r}
ggsurvplot(surv_curv_sign_lsc_pos2 ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_neg_90 signature",
          xlab="Time (Months)") 

```


## lsc negative


```{r}
vec_lsc_neg<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 < 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))
vec_lsc_neg
```

```{r}
amlcg_lsc_signature_neg<-func_signature(vec_lsc_neg,matrix_amlcg_vst,correlation_corces_lsc)
quantile(amlcg_lsc_signature_neg, c(0,.33, .66,1))

```


```{r}
amlcg_lsc_signature_neg_continuous<- cut(amlcg_lsc_signature_neg,
                       breaks=c(-10,-5.534739 ,-5.258794 , 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(amlcg_lsc_signature_neg_continuous)
```

```{r}
metadata_amlcg$sign_lsc_neg <- amlcg_lsc_signature_neg_continuous
```


#courbe OS

```{r}
surv_curv_sign_lsc_neg<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_lsc_neg , data = metadata_amlcg)
print(surv_curv_sign_lsc_neg)
```

```{r}
ggsurvplot(surv_curv_sign_lsc_neg,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, negative signature",
          xlab="Time (Months)") 
```




### courbe EFS

```{r}
surv_curv_sign_lsc_neg2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_lsc_neg , data = metadata_amlcg)
print(surv_curv_sign_lsc_neg2)
```

```{r}
ggsurvplot(surv_curv_sign_lsc_neg2 ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of AMLCG datas, LSC_neg_90 signature",
          xlab="Time (Months)") 

```