---
title: '010623_TGCA_old_data'
author: "wd"
date: '2023-02-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center",
               fig.retina = 2,
               fig.width = 10,
			         fig.height=7,
               cache = T,
               cache.lazy = F,
               echo = FALSE,
               message = FALSE,
               warning=FALSE)

```

```{r librairies, echo=FALSE, warning=FALSE}
library(readr)
library(tidyverse)

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

#BiocManager::install("DESeq2")
#BiocManager::install("apeglm")
#install.packages("DESeq2")
library(DESeq2)
library(apeglm)

library(survival)
#install.packages("survminer")
library(survminer)



theme_set(theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")
                         )
custom_theme <- theme_bw() +
        theme(
        plot.title = element_text(size=20, face="bold"),
        axis.text = element_text(size=16, color="black"), 
        axis.title = element_text(size=18,face="bold"),
        legend.title = element_text(size=18,face="bold"),
        strip.text.x = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 16),
        legend.position = "right")


```




## Importations des datas

```{r}
load("correlation_corces_aml.rda")

load("vec_top_corr_aml.rda")
load("vec_top_corr_aml_pos.rda")
load("vec_top_corr_aml_neg.rda")
```


```{r}
tcga <- read_tsv("D:/AML_processed_data/RNAseq/raw_counts/TCGA_AML_HTSeq_calc_rawcounts.txt") %>%
column_to_rownames("gene_name")
i <- colnames(tcga) 
tcga[ , i] <- apply(tcga[ , i], 2,function(x) as.integer(x))

metadata_tcga <- read_tsv("D:/AML_processed_data/RNAseq/clinical_data/TCGA_clinical_full_curated_19_06_2020.txt") %>%
column_to_rownames("Sample_ID")

inter_data<-intersect(colnames(tcga),rownames(metadata_tcga))

```

```{r}
#ligne 79

metadata_tcga<- filter(metadata_tcga, TT_type == "Intensive" & OS_MONTHS >= 0.5)
inter_data<-intersect(colnames(tcga),rownames(metadata_tcga))
```



# Préparation

151 samples (alors que 200 métadatas)


```{r analyse shrink}
data_deseq <- tcga[,inter_data]
meta_deseq <- metadata_tcga[inter_data,]

dds <- DESeqDataSetFromMatrix(countData = data_deseq, colData = meta_deseq,design = ~ Sex )

# filtration
keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]


# normalisation median of ratios method

dds <- DESeq(dds)
matrix_tcga_vst <-getVarianceStabilizedData(dds)
```


```{r}
fil_metadata_tcga<-metadata_tcga[colnames(matrix_tcga_vst),]
```

```{r}
# vec_cor_tcga<-cor(x= t(matrix_tcga_vst), y= matrix_tcga_vst['ACLY',])
# vec_cor_tcga<-as.data.frame(vec_cor_tcga)
# 
# find_pval_cor <- function(vec_nom_genes, matrix_count){
#   vec_final=c()
#   for(i in vec_nom_genes) {
#     vec_final <- append(vec_final, cor.test(matrix_count["ACLY",], y= matrix_count[i,])$p.value)
#    }
#   return(vec_final)
# }
# 
# pval_all_tcga<-find_pval_cor(row.names(matrix_tcga_vst), matrix_tcga_vst)
# vec_cor_tcga= cbind(vec_cor_tcga,pval_all_tcga)
# 
# vec_cor_tcga<- vec_cor_tcga[order(- vec_cor_tcga[,1] ), , drop= FALSE]
#   
```


```{r}

annot_tcga<-rownames(matrix_tcga_vst)
save(annot_tcga, file = "annot_tcga.rda")
```


# Signatures

```{r calcul signature}

func_signature <- function(vec_genes, mat_vst,vec_correlation){
  vec_final<- c()
  for (i in colnames(mat_vst)){
    vec_sign <- c()
    for (j in vec_genes){
      vec_sign<-append(vec_sign, mat_vst[j,i]*vec_correlation[j,"V1"])
    }
    vec_final<-append(vec_final,mean(vec_sign))
  }
  return(vec_final)
}

#essai avec les 3 signatures du groupe AML de Corces

```

##ACLY seul

```{r}
quantile(matrix_tcga_vst["ACLY",], c(0,.33, .66,1))
```

```{r}
tcga_acly_only<- cut(matrix_tcga_vst["ACLY",],
                     #breaks=quant,
                       breaks=c(0, 11.99884, 12.27266,14),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(tcga_acly_only)
```
```{r}
fil_metadata_tcga$ACLY_only<-tcga_acly_only
```
### courbe OS

```{r}
surv_curv_acly <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ ACLY_only, data = fil_metadata_tcga)
print(surv_curv_acly )
```

```{r}
ggsurvplot(surv_curv_acly,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, ACLY",
          xlab="Time (Months)")
```



### courbe EFS

```{r}
surv_curv_acly_2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ ACLY_only, data = fil_metadata_tcga)
print(surv_curv_acly_2)

```
```{r}
ggsurvplot(surv_curv_acly_2,
          #xlim = c(0,2000), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, ACLY",
          xlab="Time (Months)")
```


# Signature all samples

```{r}
load("omni_total_sign.rda")
load("correlation_corces_total.rda")
```

## Totale

```{r}
tcga_tot_signature<-func_signature(omni_total_sign,matrix_tcga_vst,correlation_corces_total)
quantile(tcga_tot_signature, c(0,.33, .66,1)) 
```
```{r}
tcga_tot_signature_continuous<- cut(tcga_tot_signature,
                       breaks=c(0, 2.435773, 2.612540, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(tcga_tot_signature_continuous)
```

```{r}
fil_metadata_tcga$sign_all_tot<-tcga_tot_signature_continuous
```

### courbe OS

```{r}
surv_curv_sign_tot_tcga <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_all_tot, data = fil_metadata_tcga)
print(surv_curv_sign_tot_tcga)
```

```{r}
ggsurvplot(surv_curv_sign_tot_tcga,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, total signature",
          xlab="Time (Months)")
```
### courbe EFS

```{r}
surv_curv_sign_tot_tcga_2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_all_tot, data = fil_metadata_tcga)
print(surv_curv_sign_tot_tcga_2)
```
```{r}
ggsurvplot(surv_curv_sign_tot_tcga_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, total signature",
          xlab="Time (Months)")
```

## sIGNATURE all samples POSITIVE

```{r}
vec_top_corr_pos<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 >= 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_pos
```

```{r}
tcga_pos_signature<-func_signature(vec_top_corr_pos,matrix_tcga_vst,correlation_corces_total)
quantile(tcga_pos_signature, c(0,.33, .66,1))
```

```{r}
tcga_pos_signature_continuous<- cut(tcga_pos_signature,
                       breaks=c(0,8.897089,9.078966, 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))
table(tcga_pos_signature_continuous)
```
### courbe OS
```{r}
fil_metadata_tcga$sign_tot_pos<-tcga_pos_signature_continuous
surv_curv_sign_pos_tcga <- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_tot_pos, data = fil_metadata_tcga)
print(surv_curv_sign_pos_tcga)
```


```{r}
ggsurvplot(surv_curv_sign_pos_tcga,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, positive signature",
          xlab="Time (Months)") 
```

### courbe EFS

```{r}
surv_curv_sign_pos_tcga_2 <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_tot_pos, data = fil_metadata_tcga)
print(surv_curv_sign_pos_tcga_2)
```

```{r}
ggsurvplot(surv_curv_sign_pos_tcga_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, positive signature",
          xlab="Time (Months)") 
```


## sIGNATURE all samples NEGATIVE

```{r}
vec_top_corr_neg<-rownames(subset(correlation_corces_total, 
                             correlation_corces_total$V1 < 0 & is.element(rownames(correlation_corces_total),omni_total_sign)))
vec_top_corr_neg
```
```{r}
tcga_neg_signature<-func_signature(vec_top_corr_neg,matrix_tcga_vst,correlation_corces_total)
quantile(tcga_neg_signature, c(0,.33, .66,1))
```
```{r}
tcga_neg_signature_continuous<- cut(tcga_neg_signature,
                       breaks=c(-10, -8.644485, -8.450537, 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(tcga_neg_signature_continuous)
```
### Courbe OS

```{r}
fil_metadata_tcga$sign_tot_neg<-tcga_neg_signature_continuous

surv_curv_sign_neg_tcga<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_tot_neg, data = fil_metadata_tcga)
print(surv_curv_sign_neg_tcga)
```


```{r}
ggsurvplot(surv_curv_sign_neg_tcga,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```

### Courbe EFS

```{r}

surv_curv_sign_neg_tcga_2<- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_tot_neg, data = fil_metadata_tcga)
print(surv_curv_sign_neg_tcga_2)
```

```{r}
ggsurvplot(surv_curv_sign_neg_tcga_2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```

# Signature AML

```{r}
load("omni_aml_tot.rda")
load("correlation_corces_aml.rda")

omni_aml_tot
```

## AML totale

```{r}
tcga_aml_signature_tot<-func_signature(omni_aml_tot,matrix_tcga_vst,correlation_corces_aml)
quantile(tcga_aml_signature_tot, c(0,.33, .66,1))
```

```{r}
tcga_aml_signature_tot_continuous<- cut(tcga_aml_signature_tot,
                       breaks=c(0, 3.122058, 3.291995  , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(tcga_aml_signature_tot_continuous)
```

```{r}
fil_metadata_tcga$sign_aml <- tcga_aml_signature_tot_continuous
```

### courbe OS

```{r}
surv_curv_aml_tot_tcga<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml, data = fil_metadata_tcga)
print(surv_curv_sign_neg_tcga)
```

```{r}
ggsurvplot(surv_curv_aml_tot_tcga,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```

### Courbe EFS

```{r}
surv_curv_aml_tot_tcga2<- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_aml, data = fil_metadata_tcga)
print(surv_curv_aml_tot_tcga2)
```

```{r}
ggsurvplot(surv_curv_aml_tot_tcga2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```

## AML positive
```{r}
vec_aml_pos<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 >= 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_pos
```

```{r}
tcga_aml_signature_pos<-func_signature(vec_aml_pos,matrix_tcga_vst,correlation_corces_aml)
quantile(tcga_aml_signature_pos, c(0,.33, .66,1))

```
```{r}
tcga_aml_signature_pos_continuous<- cut(tcga_aml_signature_pos,
                       breaks=c(0,  8.087026, 8.284492 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(tcga_aml_signature_pos_continuous)
```

```{r}
fil_metadata_tcga$sign_aml_pos <- tcga_aml_signature_pos_continuous
```


### courbe OS

```{r}
surv_curv_aml_pos_tcga<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml_pos, data = fil_metadata_tcga)
print(surv_curv_aml_pos_tcga)
```

```{r}
ggsurvplot(surv_curv_aml_pos_tcga,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```

### Courbe EFS

```{r}
surv_curv_aml_pos_tcga2<- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_aml_pos, data = fil_metadata_tcga)
print(surv_curv_aml_pos_tcga2)
```

```{r}
ggsurvplot(surv_curv_aml_pos_tcga2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```
## AML negative


```{r}
vec_aml_neg<-rownames(subset(correlation_corces_aml, 
                             correlation_corces_aml$V1 < 0 & is.element(rownames(correlation_corces_aml),omni_aml_tot)))
vec_aml_neg
```

```{r}
tcga_aml_signature_neg<-func_signature(vec_aml_neg,matrix_tcga_vst,correlation_corces_aml)
quantile(tcga_aml_signature_neg, c(0,0.33, 0.66,1))

```

```{r}
tcga_aml_signature_neg_continuous<- cut(tcga_aml_signature_neg,
                       breaks=c(-10, -7.668129, -7.487796 , 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(tcga_aml_signature_neg_continuous)
```
```{r}
fil_metadata_tcga$sign_aml_neg <- tcga_aml_signature_neg_continuous
```

### courbe OS

```{r}
surv_curv_aml_neg_tcga<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_aml_neg, data = fil_metadata_tcga)
print(surv_curv_aml_neg_tcga)
```

```{r}
ggsurvplot(surv_curv_aml_neg_tcga,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```

### Courbe EFS

```{r}
surv_curv_aml_neg_tcga2<- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_aml_neg, data = fil_metadata_tcga)
print(surv_curv_aml_neg_tcga2)
```

```{r}
ggsurvplot(surv_curv_aml_neg_tcga2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```


# Signature LSC
## LSC totale


```{r}
load("omni_LSC_tot.rda")
load("correlation_corces_lsc.rda")

omni_LSC_tot
```

```{r}
tcga_lsc_signature<-func_signature(omni_LSC_tot, matrix_tcga_vst, correlation_corces_lsc)
quantile(tcga_lsc_signature, c(0,.33, .66,1))

```

```{r}
tcga_lsc_signature_continuous<- cut(tcga_lsc_signature,
                       breaks=c(-1,  1.467496, 1.620658 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(tcga_lsc_signature_continuous)
```

```{r}
fil_metadata_tcga$lsc_tot<- tcga_lsc_signature_continuous
```


### courbe OS

```{r}
surv_curv_lsc2<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ lsc_tot, data = fil_metadata_tcga)
print(surv_curv_lsc2)
```

```{r}
ggsurvplot(surv_curv_lsc2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```




### courbe EFS

```{r}
surv_curv_lsc <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ lsc_tot, data = fil_metadata_tcga)
print(surv_curv_lsc)
```

```{r}
ggsurvplot(surv_curv_lsc,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, LSC_tot_90 signature",
          xlab="Time (Months)") 
```


## Lsc positive

```{r}
vec_lsc_pos<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 >= 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))
vec_lsc_pos
```

```{r}
tcga_lsc_signature_pos<-func_signature(vec_lsc_pos,matrix_tcga_vst,correlation_corces_lsc)
quantile(tcga_lsc_signature_pos, c(0,.33, .66,1))

```

```{r}
tcga_lsc_signature_pos_continuous<- cut(tcga_lsc_signature_pos,
                       breaks=c(0,8.435191,8.677186 , 10),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(tcga_lsc_signature_pos_continuous)
```

```{r}
fil_metadata_tcga$sign_lsc_pos <- tcga_lsc_signature_pos_continuous
```

### courbe OS

```{r}
surv_curv_lsc_pos2<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_lsc_pos, data = fil_metadata_tcga)
print(surv_curv_lsc_pos2)
```

```{r}
ggsurvplot(surv_curv_lsc_pos2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```


### courbe EFS

```{r}
surv_curv_lsc_pos <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_lsc_pos , data = fil_metadata_tcga)
print(surv_curv_lsc_pos )
```

```{r}
ggsurvplot(surv_curv_lsc_pos ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, LSC_pos_90 signature",
          xlab="Time (Months)") 
```

## Lsc negative

```{r}
vec_lsc_neg<-rownames(subset(correlation_corces_lsc, 
                             correlation_corces_lsc$V1 < 0 & is.element(rownames(correlation_corces_lsc),omni_LSC_tot)))
vec_lsc_neg
```



```{r}
tcga_lsc_signature_neg<-func_signature(vec_lsc_neg,matrix_tcga_vst,correlation_corces_lsc)
quantile(tcga_lsc_signature_neg, c(0,0.33, 0.66,1))

```

```{r}
tcga_lsc_signature_neg_continuous<- cut(tcga_lsc_signature_neg,
                       breaks=c(-10, -7.273954,-7.012136  , 0),
                       labels=c('LOW', 'MEDIUM', 'HIGH'))

table(tcga_lsc_signature_neg_continuous)
```

```{r}
fil_metadata_tcga$sign_lsc_neg <- tcga_lsc_signature_neg_continuous
```


### courbe OS

```{r}
surv_curv_lsc_neg2<- survfit(Surv(OS_MONTHS, OS_STATUS) ~ sign_lsc_neg, data = fil_metadata_tcga)
print(surv_curv_lsc_neg2)
```

```{r}
ggsurvplot(surv_curv_lsc_neg2,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, negative signature",
          xlab="Time (Months)") 
```


### courbe EFS

```{r}
surv_curv_lsc_neg <- survfit(Surv(EFS_MONTHS, EFS_STATUS) ~ sign_lsc_neg , data = fil_metadata_tcga)
print(surv_curv_lsc_neg )
```

```{r}
ggsurvplot(surv_curv_lsc_neg ,
          #xlim = c(0,67), 
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#440154", "#21918c","#fde725"),
          title="Survival analysis of TCGA datas, LSC_neg_90 signature",
          xlab="Time (Months)") 
```





